Shared Characterizations of Challenging Demands and Job Resources across O*NET Element Classifications

### 2025-07-03 Submission.Rmd
pushing to desktop

## Connecting Appraisals to Workplace Outcomes^[whole section needs reworking/reframing -- above ok 6/19/25]

The second set of predictions is focused on associations between appraisals and work outcomes. Both the job demands--resources model [@bakker2017job] as well as the challenge-hindrance stressor framework [@cavanaugh2000empirical] have been associated with a wide variety of organizational outcomes ranging from affective variables like job satisfaction, to motivation, commitment, and performance [e.g., @lepine2005meta]. The current project will focus on three outcomes: engagement, strain, and burnout. See Figure \@ref(fig:ourmodel) for proposed associations. Resources by definition include aspects of the job that may help an employee achieve work goals, reduce job demands, or promote personal growth and development [e.g., @bakker2014job; @bakker2017job], and empirical work suggests that they are associated with positive outcomes. Relevant to the current study, for example, @hakanen2008job found job resources influenced future work engagement. Moreover, in a sample of teachers and dentists, @bakker2007job found that resources were most predictive of engagement when job demands were especially high. Meta analyses have also concluded that there is a positive association with a variety of resource categories and engagement [e.g., @schaufeli2017applying].

```{r ourmodel, eval=TRUE, echo=FALSE, fig.cap="Focal constructs and associations of interest"}
library(magick)
library(grid)

@@

The findings regarding demands are more complex, presumably because the way challenge vs. hindrance appraisals influence coping strategies. Appraising a demand as a challenge has been positively associated with sources of motivation (i.e., sense of self-worth and meaningful work [@chen2021daily], engagement [@crawford2010linking], and strain and turnover intentions [e.g., @abbas2019challenge], for example. Challenge appraisals have also been negatively associated with job search behaviors [e.g., @cavanaugh2000empirical]. **CLARIFY**

When a demand is appraised as a hindrance, it is negatively associated with motivational resources [@kim2020thriving], engagement [@crawford2010linking], job search behaviors and job satisfaction [@cavanaugh2000empirical]. @chen2021daily found that daily hindrance demands were negatively associated with cognitive wellbeing and work family enrichment. Further, turnover intentions, turnover and withdrawal behaviors are negatively related to hindrance demands [@podsakoff2007differential]. Interestingly, both challenges and hindrances have been shown to positively predict strain [@abbas2019challenge; @lepine2005meta; @podsakoff2007differential; @webster2010toward], which further highlights the complex association between appraisals and subsequent outcomes. Given the differential relationships described above, we make the following predictions (see Figure \@ref(fig:ourmodel)):

>>>>

## Connecting Appraisals to Workplace Outcomes

Both the job demands--resources model [@bakker2017job] as well as the challenge--hindrance stressor framework [@cavanaugh2000empirical] have been useful in the prediction of a wide variety of organizational outcomes including job satisfaction, motivation, commitment, and performance [e.g., @lepine2005meta]. Empirical work generally suggests that *resources* are commonly associated with positive outcomes, including, most relevant for the current investigation, employee engagement. For example, @hakanen2008job found that job resources influenced future work engagement. Moreover, in a sample of teachers and dentists, @bakker2007job found that resources were most predictive of engagement when job demands were especially high. Meta analyses have also concluded that there is a positive association with a variety of resource elements and engagement [e.g., @schaufeli2017applying].

```{r ourmodel, eval=TRUE, echo=FALSE, fig.cap="Focal constructs and predicted associations"}
library(magick)
library(grid)

@@

The findings regarding demands are more complex. When a demand is appraised as a hindrance, it is negatively associated with motivational resources [@kim2020thriving], engagement [@crawford2010linking], job search behaviors, and job satisfaction [@cavanaugh2000empirical]. @chen2021daily further found that daily hindrance demands were negatively associated with cognitive wellbeing and work family enrichment. Turnover intentions, actual turnover and withdrawal behaviors have also been associated with hindrance demands [@podsakoff2007differential]. Appraising a demand as a *challenge*, however, has been positively associated with sources of motivation (i.e., sense of self-worth and meaningful work, @chen2021daily, engagement, @crawford2010linking, and strain and turnover intentions, e.g., @abbas2019challenge). Challenge appraisals have also been found to ehave negative associations with job search behaviors [e.g., @cavanaugh2000empirical]. Interestingly, both challenges and hindrances have been shown to positively predict strain [@abbas2019challenge; @lepine2005meta; @podsakoff2007differential; @webster2010toward], which further highlights the complex association between characteristic appraisals and important work outcomes. Given the differential relationships described above, and a focus on three outcomes (engagement, strain, and burnout) we make the following predictions (see Figure \@ref(fig:ourmodel)):

### 2025-07-03 Submission.tex
pushing to desktop

\hypertarget{connecting-appraisals-to-workplace-outcomes}{%
\subsection[Connecting Appraisals to Workplace Outcomes]{\texorpdfstring{Connecting Appraisals to Workplace Outcomes\footnote{whole section needs reworking/reframing -- above ok 6/19/25}}{Connecting Appraisals to Workplace Outcomes}}\label{connecting-appraisals-to-workplace-outcomes}}

The second set of predictions is focused on associations between appraisals and work outcomes. Both the job demands--resources model (Bakker and Demerouti, 2017) as well as the challenge-hindrance stressor framework (Cavanaugh et al., 2000) have been associated with a wide variety of organizational outcomes ranging from affective variables like job satisfaction, to motivation, commitment, and performance (e.g., LePine et al., 2005). The current project will focus on three outcomes: engagement, strain, and burnout. See Figure \ref{fig:ourmodel} for proposed associations. Resources by definition include aspects of the job that may help an employee achieve work goals, reduce job demands, or promote personal growth and development (e.g., Bakker and Demerouti, 2014, 2017), and empirical work suggests that they are associated with positive outcomes. Relevant to the current study, for example, Hakanen et al. (2008) found job resources influenced future work engagement. Moreover, in a sample of teachers and dentists, Bakker et al. (2007) found that resources were most predictive of engagement when job demands were especially high. Meta analyses have also concluded that there is a positive association with a variety of resource categories and engagement (e.g., Schaufeli, 2017).

\begin{figure}
\centering
\includegraphics{Submission_files/figure-latex/ourmodel-1.pdf}
\caption{\label{fig:ourmodel}Focal constructs and associations of interest}
\end{figure}

The findings regarding demands are more complex, presumably because the way challenge vs.~hindrance appraisals influence coping strategies. Appraising a demand as a challenge has been positively associated with sources of motivation (i.e., sense of self-worth and meaningful work (Chen et al., 2021), engagement (Crawford et al., 2010), and strain and turnover intentions (e.g., Abbas and Raja, 2019), for example. Challenge appraisals have also been negatively associated with job search behaviors (e.g., Cavanaugh et al., 2000). \textbf{CLARIFY}

When a demand is appraised as a hindrance, it is negatively associated with motivational resources (Kim and Beehr, 2020), engagement (Crawford et al., 2010), job search behaviors and job satisfaction (Cavanaugh et al., 2000). Chen et al. (2021) found that daily hindrance demands were negatively associated with cognitive wellbeing and work family enrichment. Further, turnover intentions, turnover and withdrawal behaviors are negatively related to hindrance demands (Podsakoff et al., 2007). Interestingly, both challenges and hindrances have been shown to positively predict strain (Abbas and Raja, 2019; LePine et al., 2005; Podsakoff et al., 2007; Webster et al., 2010), which further highlights the complex association between appraisals and subsequent outcomes. Given the differential relationships described above, we make the following predictions (see Figure \ref{fig:ourmodel}):

>>>>

\hypertarget{connecting-appraisals-to-workplace-outcomes}{%
\subsection{Connecting Appraisals to Workplace Outcomes}\label{connecting-appraisals-to-workplace-outcomes}}

Both the job demands--resources model (Bakker and Demerouti, 2017) as well as the challenge--hindrance stressor framework (Cavanaugh et al., 2000) have been useful in the prediction of a wide variety of organizational outcomes including job satisfaction, motivation, commitment, and performance (e.g., LePine et al., 2005). Empirical work generally suggests that \emph{resources} are commonly associated with positive outcomes, including, most relevant for the current investigation, employee engagement. For example, Hakanen et al. (2008) found that job resources influenced future work engagement. Moreover, in a sample of teachers and dentists, Bakker et al. (2007) found that resources were most predictive of engagement when job demands were especially high. Meta analyses have also concluded that there is a positive association with a variety of resource elements and engagement (e.g., Schaufeli, 2017).

\begin{figure}
\centering
\includegraphics{Submission_files/figure-latex/ourmodel-1.pdf}
\caption{\label{fig:ourmodel}Focal constructs and predicted associations}
\end{figure}

The findings regarding demands are more complex. When a demand is appraised as a hindrance, it is negatively associated with motivational resources (Kim and Beehr, 2020), engagement (Crawford et al., 2010), job search behaviors, and job satisfaction (Cavanaugh et al., 2000). Chen et al. (2021) further found that daily hindrance demands were negatively associated with cognitive wellbeing and work family enrichment. Turnover intentions, actual turnover and withdrawal behaviors have also been associated with hindrance demands (Podsakoff et al., 2007). Appraising a demand as a \emph{challenge}, however, has been positively associated with sources of motivation (i.e., sense of self-worth and meaningful work, Chen et al. (2021), engagement, Crawford et al. (2010), and strain and turnover intentions, e.g., Abbas and Raja (2019)). Challenge appraisals have also been found to ehave negative associations with job search behaviors (e.g., Cavanaugh et al., 2000). Interestingly, both challenges and hindrances have been shown to positively predict strain (Abbas and Raja, 2019; LePine et al., 2005; Podsakoff et al., 2007; Webster et al., 2010), which further highlights the complex association between characteristic appraisals and important work outcomes. Given the differential relationships described above, and a focus on three outcomes (engagement, strain, and burnout) we make the following predictions (see Figure \ref{fig:ourmodel}):
